---
title: "Elementary presentation of differences between R sessions"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Elementary presentation of differences between R sessions}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

```{r setup,echo=FALSE,message=FALSE}
library(sessdiff)
```

# sessdiff -- package/version differences between sessions

The `sessioninfo` package manages `sessionInfo()` outputs
and facilitates programmatic analysis of R sessions.

The `session_diff` function provided there produces fairly
elaborate reports.  This package has a single function that
extracts package and version information for
packages present in one but not another session.

In our first example, we show how identical
sessions are identified:

```{r doexa}
library(sessdiff)
si = sessioninfo::session_info()
sessdiff(si, si)
```

In the second example, we show how loading
a package affects the comparison.

```{r doex2}
requireNamespace("parody") # unlikely to be loaded
si2 = sessioninfo::session_info()
sessdiff(si, si2)
```

# Further work

External resources like python configurations and numerical library
versions can be obtained using `sessioninfo` functions.  It will
likely be useful to have simple reports on differences in
these aspects of session configuration.
